---
title: "Upload a File to DataStore"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Upload a File to DataStore}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(NPSdatastore)
```

## Before you start

Before attempting to upload a file to a DataStore reference, there are some
conditions that need to be met.

1. Make sure you have edit permissions to the DataStore reference.
2. Make sure the reference permits uploads. Certain types of reference, such as
programs and projects, are designed to be containers for organizing other 
references and therefore cannot directly contain files.
3. Make sure you are on the internal NPS network.

## Testing

Consider using [https://irmadev.nps.gov/DataStore]

## Uploading the file

You'll need the following information:

- The location of the file on your hard drive. Make sure that the path includes
the name of the file (not just the folder it lives in), and be sure that the
slashes in the path are either single forward slashes (/) or double backslashes
(\\).
- The reference ID of the DataStore reference you are uploading to. When you
navigate to your reference in a web browser, the URL will look something like
this: "https://irma.nps.gov/DataStore/Reference/Profile/1234567". The number
at the end of the URL (in this example, 1234567) is your reference ID.
- Whether the file is 508-compliant.

Set that information using the code template below:

```{r args, eval = FALSE}
file_to_upload <- "C:/your/file/location/here.csv"
reference_id <- 1234567  # Replace this with your reference ID
is_508_compliant <- FALSE  # If you know your file is 508 compliant, change to TRUE
```

Double-check your reference ID! If it's incorrect, your file upload will either
fail, or the file could end up in the wrong reference.

Double-check your file path! Make sure it's correct, and make sure you aren't
uploading sensitive data to a public reference.

Once you are certain everything is correct, perform the file upload:

```{r upload, eval = FALSE}
result <- upload_file_to_reference(reference_id = reference_id,
                                   file_path = file_to_upload, 
                                   is_508 = is_508_compliant,
                                   dev = FALSE)
```


